\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{datetime}
\usdate
\usepackage{nicefrac}

%% fonts
\usepackage{mathptmx,courier,textcomp}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xfrac}


\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}


%
% Some new commands I use in this text
%
% Note:
% Nice curly font is {\bm{\mathcal{D}}}
%
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\abbrev}[1]{\rm{#1}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images
\newcommand{\fix}[2]{\st{#1}\hl{#2}}

%
% Used symbols (only partial for now...)
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
\newcommand{\OpDistance}{\bm{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\MaskSun}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
\newcommand{\OpDiag}[1]{\mathbb{D}\left\{#1\right\}}
\newcommand{\DistSet}{\mathcal{C}}
\newcommand{\DistUnknown}{\vect{n}}
\newcommand{\DistEstimated}{\hat{\vect{n}}}
\newcommand{\CostFunc}[1]{E(#1)}


\topmargin      -0.0truein%do not change
\oddsidemargin   0.0truein%do not change
\evensidemargin  0.0truein%do not change
\textheight     8.5truein%do not change
\textwidth      6.3truein%do not change

\parskip 0.3cm
\parindent=0pt

%\pagestyle{empty}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace*{.5cm} \hrule

\def\sender{
  \it{Amit Aides}\\
  \scriptsize{Dept. of Electrical Engineering, Technion - Israel Inst.~Technology, Haifa 32000, Israel.}\\
  \scriptsize{Tel No.: (+972) 54-4526416}\hspace{5pt}\\
  \scriptsize{E-mail: amitibo@tx.technion.ac.il} } {\sender}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{0.5cm}
\noindent
To:\\
Production Editor, Optics Express\\[0.6cm]

\begin{flushright}
  \today
\end{flushright}

\vspace{0.3cm} \noindent

Dear production editor,

Thank you for accepting our manuscript for publication.
We have applied the required formatting changes. In order to correct
the citation order of Fig. 9, we moved the figure into section 6 of
the article. This change required us to re-arange the order of figures
in this section (section 6) and make minor changes to the body of 
the text.
We made minor textual corrections in several other locations, to smooth
the flow. Specifically, in the abstract we moved the reference of
"visibile light" from sentence 3 to sentence 6; we refer to Fig.3
in the begining of Sec.5; we inserted our prior footnote into the main text
of Sec.5; and we wrote a corrected ackowlegements.

Is it possible to receive the proof, before you publish, so we
verify and approve that all is in order?\\

\vspace{0.2cm} Sincerely,

\vspace{0.6cm}
Amit Aides, corresponding author.\\

\end{document}
